---
title: "Babynames with Shiny Parameters"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(magrittr)
library(babynames)
library(flexdashboard)

comparison_name <- "Garrett"
comparison_gender <- "M"

theme_set(theme_minimal())
```

# Description

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `textInput`, `selectInput`, and `sliderInput` functions create the input widgets used to drive the plot.

## Column {data-width=200}

### Inputs

```{r inputs, echo=FALSE}
inputPanel(
  textInput("name", label = "Name", value = "Carl"),
  selectInput("gender", label = "Gender",
              choices = c("M", "F"), selected = "M"),
  sliderInput("range", "Range:",
                  min = 1880, max = 2017,
                  value = c(1880,2017),
                  sep = ""
              )
  )
```

## Column {data-width=600}

### Popularity Graph

```{r echo = FALSE, message = FALSE, warning = FALSE, out.width = "90%"}

renderPlot({
  dataset <- babynames %>% 
    filter(    (name == "Garrett" & sex == "M") |
               (name == input$name & sex == input$gender)) %>% 
    filter(year >= input$range[1] & year <= input$range[2])
  
  p <-  ggplot(dataset) +
    geom_line(aes(x = year, y = prop, group = name, color = name)) +
    ggtitle(paste0("Proportional popularity of ", comparison_name,
                   " versus ", input$name,
                   " from ", input$range[1],
                   " to ", input$range[2]))
  
  print(p)
})
