---
title: "Post-process R plots from code chunks"
author: "Frank Dobie"
output:
  html_document:
    self_contained: false
---

The chunk option `fig.process` is a function that takes the figure file path and the list chunk options as the input, and returns a (new) file path of the figure.

## A (relatively) simple example:

```{r}
rename_fig = function(x, options) {
  # just for you to better understand what x is
  message('The original filename is ', x)
  # new name
  x2 = gsub('-1.png', '.png', x)
  message('The new filename will be ', x2)
  file.rename(x, x2)
  x2
}
```

Try the above function:

```{r, cars, fig.process=rename_fig}
plot(cars)
```

Now we present more complicated examples.

```{r, include=FALSE}
knitr::opts_chunk$set(fig.retina = 1)
xfun::pkg_load2('magick')  # install magick if not already installed
```

A figure processing function based on **magick** (you can specify the **magick** function via the chunk option `magick.fun`, and arguments via the chunk option `magick.args`):

```{r}
magick_proc = function(x, options) {
  FUN = options$magick.fun
  if (is.null(FUN)) FUN = magick::image_blur
  img = magick::image_read(x)
  res = do.call(FUN, c(list(img), options$magick.args))
  magick::image_write(res, x)
  x
}
```

# The orginal plot

```{r, orig}
dat = iris[, 1:2]
par(mar = c(4, 4, .1, .2))
smoothScatter(dat)
sunflowerplot(dat, pch = 20, col = 7, seg.col = 7, size = .1, add = TRUE)
```

# Blurred version

```{r, blur, ref.label='orig', fig.process=magick_proc, magick.args=list(radius = 10, sigma = 5)}
```

# The charcoal effect

```{r, charcoal, ref.label='orig', fig.process=magick_proc, magick.fun=magick::image_charcoal}
```

# Negate it

```{r, negate, ref.label='orig', fig.process=magick_proc, magick.fun=magick::image_negate}
```

# A figure processing function to add an R logo to your plots

```{r}
add_logo = function(x, options) {
  # the plot created from the code chunk
  img = magick::image_read(x)
  # the R logo
  logo = file.path(R.home("doc"), "html", "logo.jpg")
  logo = magick::image_read(logo)
  # the default gravity is northwest, and users can change it via the chunk
  # option magick.gravity
  if (is.null(g <- options$magick.gravity)) g = 'northwest'
  # add the logo to the plot
  img = magick::image_composite(img, logo, gravity = g)
  # write out the new image 
  magick::image_write(img, x)
  x
}
```

Test the `add_logo()` function:

```{r, logo, ref.label='orig', fig.process=add_logo}
```

Add the logo to the northeast corner:

```{r, logo-ne, ref.label='orig', fig.process=add_logo, magick.gravity='northeast'}
```
